Is Google Translate Sexist? -- Assessing Gender Bias in Machine Translation

### 2017-12-18 paper/main.tex
Fixed references

\usepackage[utf8]{inputenc}
%\usepackage{fontspec}
\usepackage{xeCJK}

@@

\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|}
	\hline
	Language 	& Sentence template \\ \hline \hline
	Malay		& dia adalah $\langle occupation \rangle$ \\ \hline
	Estonian	& ta on $\langle occupation \rangle$ \\ \hline
	Finnish		& hän on $\langle occupation \rangle$ \\ \hline
	Hungarian	& ő $\langle occupation \rangle$ \\ \hline
	Armenian	& նա $\langle occupation \rangle$ է \\ \hline
	Japanese	& $\langle occupation \rangle$ です\\ \hline
	Turkish		& o bir $\langle occupation \rangle$ \\ \hline
	Yoruba		& o jẹ $\langle occupation \rangle$ \\ \hline
	Basque		& $\langle occupation \rangle$ da \\ \hline
	Swahili		& yeye ni $\langle occupation \rangle$ \\ \hline
	Chinese		& ta $\langle occupation \rangle$ \\ \hline
	\end{tabular}
	\caption{Templates used to infer gender biases in the translation to the English language.}
	\label{tab:templates}
\end{table}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{pictures/gender-by-language}
	\label{fig:gender-by-language}
	\caption{The distribution of pronominal genders per language also suggests a tendency towards male defaults, with female pronouns reaching as low as $0.46\%$ and $2.98\%$ for Japanese and Chinese respectively. Once again not all bars add up to $100\%$ as Google Translate occasionally fails to translate sentences, particularly in Japanese and Basque. Among all tested languages, Basque was the only one to yield more gender neutral than male pronouns.}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{pictures/scatterplot-languages}
	\label{fig:scatterplot-languages}
	\caption{Scatter plot of translated sentences' statistics. Each point (color coded according to its category) corresponds to a single occupation, of which the sex ratio and the percentage of gender neutral pronouns are averaged over all tested languages (Malay, Estonian, Finnish, Hungarian, Armenian, Japanese, Turkish, Yoruba, Basque, Swahili and Chinese).}
\end{figure}

>>>>

\usepackage[utf8]{inputenc}
%\usepackage{fontspec}
\usepackage{xeCJK}
%\usepackage{armtex}

@@

\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|}
	\hline
	Language 	& Sentence template \\ \hline \hline
	Malay		& dia adalah $\langle occupation \rangle$ \\ \hline
	Estonian	& ta on $\langle occupation \rangle$ \\ \hline
	Finnish		& hän on $\langle occupation \rangle$ \\ \hline
	Hungarian	& ő $\langle occupation \rangle$ \\ \hline
	Armenian	& na $\langle occupation \rangle$ e \\ \hline
	Japanese	& $\langle occupation \rangle$ です\\ \hline
	Turkish		& o bir $\langle occupation \rangle$ \\ \hline
	Yoruba		& o jẹ $\langle occupation \rangle$ \\ \hline
	Basque		& $\langle occupation \rangle$ da \\ \hline
	Swahili		& yeye ni $\langle occupation \rangle$ \\ \hline
	Chinese		& ta $\langle occupation \rangle$ \\ \hline
	\end{tabular}
	\caption{Templates used to infer gender biases in the translation to the English language.}
	\label{tab:templates}
\end{table}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{pictures/gender-by-language}
	\caption{The distribution of pronominal genders per language also suggests a tendency towards male defaults, with female pronouns reaching as low as $0.46\%$ and $2.98\%$ for Japanese and Chinese respectively. Once again not all bars add up to $100\%$ as Google Translate occasionally fails to translate sentences, particularly in Japanese and Basque. Among all tested languages, Basque was the only one to yield more gender neutral than male pronouns.}
	\label{fig:gender-by-language}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{pictures/scatterplot-languages}
	\caption{Scatter plot of translated sentences' statistics. Each point (color coded according to its category) corresponds to a single occupation, of which the sex ratio and the percentage of gender neutral pronouns are averaged over all tested languages (Malay, Estonian, Finnish, Hungarian, Armenian, Japanese, Turkish, Yoruba, Basque, Swahili and Chinese).}
	\label{fig:scatterplot-languages}
\end{figure}
